---
title: "Internetnutzung"
author: "Sophie Hensgen"
date: "3/1/2021"
output: html_document
---
## Load required packages

```{r packages, include=FALSE}

library(pdftools)
library(glue)
library(tidyverse)
library(ggthemes)
library(tabulizer)
library(dplyr)
```

## Download Data from PDF

Next create a vector of PDF file names using the list.files function. The pattern argument says to only grab those files ending with “pdf”:

```{r pdf, echo=FALSE}

files <- list.files(pattern = "pdf$")

```

## Lapply

We’ll use this vector to automate the process of reading in the text of the PDF files.

The pdftools function for extracting text is pdf_text. Using the lapply function, we can apply the pdf_text function to each element in the “files” vector and create an object called “opinions”.

```{r lapply}
opinions <- lapply(files, pdf_text)

lapply(opinions, length) 
str(opinions)

```

## Store each PDF in an object

Cleaning Data from 2016-2020

```{r einzelne pdfs}
ikt.16 <- opinions[[1]]
ikt.17 <- opinions[[2]]
ikt.18 <- opinions[[3]]
ikt.19 <- opinions[[4]]
ikt.20 <- opinions[[5]]
```

## Start Cleaning Data with 2016


```{r einzelne pdfs}
# interessante Tabelle auf Seite 13
#ikt.16 
#cat(ikt.16[13])

table <- ikt.16[13]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1 Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 38,39,112,185,246,247,286,297)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
t <- gsub("\n", "", t)

b <- list()
for(i in 1:12){
  b[[i]] <- t[seq(i, length(t), 12)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2016) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
df$`Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl` <- NA
df$`Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000` <- NA
df <- df[c(1,2,3,4,5,6,7,8,9,10,17,18,11,12,13,14,15,16)]
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df16 <- df
df16

```

## Save Data Frame for 2016


```{r Save Data Frame}

# Store dataframe as csv style
write.csv(df16,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.16.csv", row.names = FALSE)

```

## Start Cleaning Data with 2017


```{r einzelne pdfs}
#ikt.17

table <- ikt.17[14]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1 Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 44, 45, 130, 215, 286, 287, 332, 345)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
t <- gsub("\n", "", t)

b <- list()
for(i in 1:14){
  b[[i]] <- t[seq(i, length(t), 14)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]], b[[13]], b[[14]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2017) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
  
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df17 <- df
df17

```

## Save Data Frame for 2017


```{r Save Data Frame}

# Store dataframe as csv style
write.csv(df17,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.17.csv", row.names = FALSE)

```

## Start Cleaning Data with 2018


```{r einzelne pdfs}
# ikt.18

table <- ikt.18[12]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1) Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 44, 45, 130, 215, 286, 287, 332, 345, 346)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
t <- gsub("\n", "", t)

b <- list()
for(i in 1:14){
  b[[i]] <- t[seq(i, length(t), 14)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]], b[[13]], b[[14]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2018) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
  
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df18 <- df
df18

```

## Save Data Frame for 2018


```{r Save Data Frame}

# Store dataframe as csv style
write.csv(df18,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.18.csv", row.names = FALSE)

```

## Start Cleaning Data with 2019


```{r einzelne pdfs}
ikt.19

table <- ikt.19[13]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1) Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 44, 45, 130, 215, 286, 287, 332, 345, 346)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
t <- gsub("\n", "", t)

b <- list()
for(i in 1:14){
  b[[i]] <- t[seq(i, length(t), 14)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]], b[[13]], b[[14]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2019) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
  
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df19 <- df
df19

```

## Save Data Frame for 2019


```{r Save Data Frame}

# Store dataframe as csv style
write.csv(df19,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.19.csv", row.names = FALSE)

```



## Start Cleaning Data with 2020


```{r einzelne pdfs}
ikt.20

table <- ikt.20[12]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1) Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 44, 45, 130, 215, 286, 287, 332, 345, 346)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
t <- gsub("\n", "", t)

b <- list()
for(i in 1:14){
  b[[i]] <- t[seq(i, length(t), 14)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]], b[[13]], b[[14]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2020) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
  
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df20 <- df
df20

```

## Save Data Frame for 2020


```{r Save Data Frame}

# Store dataframe as csv style
write.csv(df20,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.20.csv", row.names = FALSE)

```

## Combine data frames into one

```{r combine data frames}

# Combine all years into one

df <- rbind(df16, df17, df18, df19, df20)

# get rid of whitespacing in order to change type
df$`Alle Personen: erfasste Anzahl` <- gsub(" ", "", df$`Alle Personen: erfasste Anzahl`)
df$`Alle Personen: hochgerechnet 1000` <- gsub(" ", "", df$`Alle Personen: hochgerechnet 1000`)
df$`Internetnutzer/-innen: erfasste Anzahl` <- gsub(" ", "", df$`Alle Personen: hochgerechnet 1000`)
df$`Internetnutzer/-innen: hochgerechnet 1000`<- gsub(" ", "", df$`Internetnutzer/-innen: hochgerechnet 1000`)
df$`Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl`<- gsub(" ", "", df$`Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl`)
df$`Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000`<- gsub(" ", "", df$`Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000`)
df$`Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl`<- gsub(" ", "", df$`Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl`)
df$`Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000`<- gsub(" ", "", df$`Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000`)
df$`Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl`<- gsub(" ", "", df$`Online-EInkäufer/-innen letzte 3 Monate: erfasste Anzahl`)
df$`Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000`<- gsub(" ", "", df$`Online-EInkäufer/-innen letzte 3 Monate: hochgerechnet 1000`)
df$`Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl`<- gsub(" ", "", df$`Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl`)
df$`Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000`<- gsub(" ", "", df$`Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000`)



df[, c(1, 3:14, 16)] <- sapply(df[, c(1, 3:14, 16)], as.numeric)
df

```

## Save final Data Frame


```{r Save Data Frame}

# Store dataframe as csv style

write.csv(df,"/Users/sophiehensgen/Github-Projects/Internetnutzung_Deutschland/internet.final.csv", row.names = FALSE)

```









