---
title: "Internetnutzung"
author: "Sophie Hensgen"
date: "3/1/2021"
output: html_document
---
## Load required packages

```{r packages, include=FALSE}

library(pdftools)
library(glue)
library(tidyverse)
library(ggthemes)
library(tabulizer)
```

## Download Data from PDF

Next create a vector of PDF file names using the list.files function. The pattern argument says to only grab those files ending with “pdf”:

```{r pdf, echo=FALSE}

files <- list.files(pattern = "pdf$")

```

## Lapply

We’ll use this vector to automate the process of reading in the text of the PDF files.

The pdftools function for extracting text is pdf_text. Using the lapply function, we can apply the pdf_text function to each element in the “files” vector and create an object called “opinions”.

```{r lapply}
opinions <- lapply(files, pdf_text)

lapply(opinions, length) 
str(opinions)

```

## Store each PDF in an object

Cleaning Data from 2016-2020

```{r einzelne pdfs}
ikt.16 <- opinions[[1]]
ikt.17 <- opinions[[2]]
ikt.18 <- opinions[[3]]
ikt.19 <- opinions[[4]]
ikt.20 <- opinions[[5]]
```

## Start Cleaning Data with 2016


```{r einzelne pdfs}
# interessante Tabelle auf Seite 13
#ikt.16 
#cat(ikt.16[13])

table <- ikt.16[13]

# Delete the collumns for easy access
t <- gsub(".*10 Jahren", "", table) # delete everything before 10 Jahren
t <- gsub("1 Einschließlich.*$", "", t) # delete everything after 1 Einschließlich
t <- unlist(strsplit(t, split = "\\s{2,}")) # split into individual characters

t <- t[-c(1, 38,39,112,185,246,247,286,297)] # delete first element 
t <- gsub("Rentner/-innen und andere", "Rentner/-innen und andere nicht erwerbstätige Personen", t)
t <- gsub("10 - 15", "Alter: 10 - 15", t)
t <- gsub("16 - 24", "Alter: 16 - 24", t)
t <- gsub("25 - 44", "Alter: 25 - 44", t)
t <- gsub("45 - 64", "Alter: 45 - 64", t)
t <- gsub("65 Jahre und älter", "Alter: 65 Jahre und älter.", t)
t <- gsub("\\.", "", t)
t <- gsub("Männlich", "Männlich - Komplett", t)
t <- gsub("Weiblich", "Weiblich - Komplett", t)
t <- gsub("Niedrig", "Bildungsstand - Niedrig", t)
t <- gsub("Mittel", "Bildungsstand - Mittel", t)
t <- gsub("Hoch", "Bildungsstand - Hoch", t)
b <- list()

for(i in 1:12){
  b[[i]] <- t[seq(i, length(t), 12)] # loop to create individual columns per list
}

df <- data.frame(b[[1]], b[[2]],  b[[3]], b[[4]], b[[5]], b[[6]], b[[7]], b[[8]], b[[9]], b[[10]], b[[11]], b[[12]]) # Create data frame

df$StartingAge <- c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 10, 16, 16, 16, 16, 16, 16, 16) # add column which says what the asking age was
df$SurvYear <- c(2016) # add column with survey year
df$Geschlecht <- c("Total", "Total", "Total", "Total", "Total", "Total", "Total", "Total", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Männlich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Weiblich", "Total", "Total", "Total", "Total", "Total", "Total", "Total")
df$GeschlechtNum <- ifelse(df$Geschlecht == "Total", 3, ifelse(df$Geschlecht == "Männlich", 1, 2))
  
colnames(df) <- c("Lfd. Nr.", "Gegenstand der Nachweisung", "Alle Personen: erfasste Anzahl", "Alle Personen: hochgerechnet 1000", "Internetnutzer/-innen: erfasste Anzahl", "Internetnutzer/-innen: hochgerechnet 1000", "Internetnutzer/-innen letzte 3 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 3 Monate: hochgerechnet 1000", "Internetnutzer/-innen letzte 12 Monate: erfasste Anzahl", "Internetnutzer/-innen letzte 12 Monate: hochgerechnet 1000", "Online-EInkäufer/-innen letzte 12 Monate: erfasste Anzahl", "Online-EInkäufer/-innen letzte 12 Monate: hochgerechnet 1000", "StartingAge", "SurvYear", "Geschlecht", "GeschlechtNum")

df

str(df)
```

## Start Cleaning Data with 2017


```{r einzelne pdfs}
ikt.17

gesamt <- ikt.17[13]

```

## Start Cleaning Data with 2018


```{r einzelne pdfs}
ikt.18

gesamt <- ikt.18[13]

```

## Start Cleaning Data with 2019


```{r einzelne pdfs}
ikt.19

gesamt <- ikt.19[13]

```

## Start Cleaning Data with 2020


```{r einzelne pdfs}
ikt.20

gesamt <- ikt.20[13]

```














