---
title: "Internetnutzung"
author: "Sophie Hensgen"
date: "3/1/2021"
output: html_document
---

```{r packages, include=FALSE}

library(pdftools)
library("glue")
library("tidyverse")
library("ggthemes")
library(tabulizer)
```

## Download Data from PDF

Next create a vector of PDF file names using the list.files function. The pattern argument says to only grab those files ending with “pdf”:

```{r pdf, echo=FALSE}

files <- list.files(pattern = "pdf$")

```

## Lapply

We’ll use this vector to automate the process of reading in the text of the PDF files.

The pdftools function for extracting text is pdf_text. Using the lapply function, we can apply the pdf_text function to each element in the “files” vector and create an object called “opinions”.

```{r lapply}
opinions <- lapply(files, pdf_text)

lapply(opinions, length) 
str(opinions)
```

## Cleaning Data

Clean Data from 2020

```{r einzelne pdfs}
ikt.16 <- opinions[[1]]
ikt.17 <- opinions[[2]]
ikt.18 <- opinions[[3]]
ikt.19 <- opinions[[4]]
ikt.20 <- opinions[[5]]
```

## Start Cleaning Data with 2016


```{r einzelne pdfs}
ikt.16 

gesamt <- ikt.16[13]

table <- str_replace_all(gesamt, "\\s{2,}", "|")
table <- gsub("^.*?Jahren.","",table)
table

read.table(text=gsub("(?<=[a-z])\\s+", "\n", table, perl=TRUE), 
            header=TRUE)
col.names = c("lfd Nr.", "Gegenstand der Nachweisung", "erfasst", "hochgerechnet", "erfasst", "hochgerechnet", "erfasst", "hochgerechnet", "erfasst", "hochgerechnet", "erfasst", "hochgerechnet")

clean_table <- function(table){
    table <- str_split(table, "\n", simplify = TRUE)
    #country_name <- table[1, 1] %>% 
      #  stringr::str_squish() %>% 
       # stringr::str_extract(".+?(?=\\sTotal)")
    table_start <- stringr::str_which(table, "Erfasste Haushalte")
    table_end <- stringr::str_which(table, "11 472")
    #table <- table[1, (table_start +1 ):(table_end - 1)]
    table <- str_replace_all(table, "\\s{2,}", "|")
    text_con <- textConnection(table)
    data_table <- read.csv(text_con, sep = "|")
    #colnames(data_table) <- c("h", "Number", "Gegenstand der Nachweisung", "Mitte", "Deutschland", "Früheres Bundesgebiet", "Neue Länder und Berlin")
    #dplyr::mutate(data_table, Country = country_name)
}
```

## Start Cleaning Data with 2017


```{r einzelne pdfs}
ikt.17

gesamt <- ikt.17[13]

```

## Start Cleaning Data with 2018


```{r einzelne pdfs}
ikt.18

gesamt <- ikt.18[13]

```

## Start Cleaning Data with 2019


```{r einzelne pdfs}
ikt.19

gesamt <- ikt.19[13]

```

## Start Cleaning Data with 2020


```{r einzelne pdfs}
ikt.20

gesamt <- ikt.20[13]

```

## Cleaning ikt.11


```{r einzelne pdfs}
# ab 7 fangen die Tabellen an bis 76


clean_table <- function(table){
    table <- str_split(table, "\n", simplify = TRUE)
    #country_name <- table[1, 1] %>% 
      #  stringr::str_squish() %>% 
       # stringr::str_extract(".+?(?=\\sTotal)")
    table_start <- stringr::str_which(table, "Erfasste Haushalte")
    table_end <- stringr::str_which(table, "/  ")
    #table <- table[1, (table_start +1 ):(table_end - 1)]
    table <- str_replace_all(table, "\\s{2,}", "|")
    text_con <- textConnection(table)
    data_table <- read.csv(text_con, sep = "|")
    #colnames(data_table) <- c("h", "Number", "Gegenstand der Nachweisung", "Mitte", "Deutschland", "Früheres Bundesgebiet", "Neue Länder und Berlin")
    #dplyr::mutate(data_table, Country = country_name)
}

clean_table(ikt.11[7])
clean <- ikt.11[7]
clean <- str_split(ikt.11[7], "\n", simplify = TRUE)

 table <- str_replace_all(clean, "\\s{2,}", "|")
 clean <- str_split(table, "\n", simplify = TRUE)
```












